InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-08 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

As this is a very topical issue the "Gesellschaft für Informatik" \cite{GI} organizes a competition called "InformatiCup2024" \cite{InformatiCup} in which the topic is to manipulate a detectable source in a way that the detector does not recognize it anymore. This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g. images and texts) to reduce the accuracy of detectors.

>>>>

As this is a very topical issue the "Gesellschaft für Informatik" \cite{GI} organizes a competition called "InformatiCup2024" \cite{InformatiCup} in which the topic is to manipulate a detectable source in a way that the detector does not recognize it as AI-generated anymore. This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g. images and texts) to reduce the accuracy of detectors.
